# Homework I -- Econometrics I 2024/25 Fall


Q-01) Add the command which clears the environment
```{r, eval = FALSE}
# Clear environment
```

Q-02) Create a string variable, which states: `This is my first assignment in R!`

```{r, eval = FALSE}
str_var <-
```

Q-03) Create vector `gdppc`, which contains the values of: 12, 18, 25, 13, 16 and 14 
```{r, eval = FALSE}
gdppc <-
```

Q-04) Multiply this vector with 10,000 and name it as `gdppc_10`
```{r, eval = FALSE}
gdppc_10 <-
```

Q-05) Create an other vector called `lifeexp` with values of: 62, 68, 73, 65, 66 and 69
```{r, eval = FALSE}
lifeexp <-
```

Q-06) Calculate the average of lifeexp as `avg_le`
```{r, eval = FALSE}
avg_le <-
```

Q-07) Calculate the average of gdppc as `avg_gdppc`
```{r, eval = FALSE}
avg_gdppc <-
```

Q-08) Store the two vectors in a `data.frame()` object and call it `df`. Use their names for colnames.
```{r, eval = FALSE}
df <-
```

Q-09) Calculate the covariance matrix of `df` with the function `cov()` and name it as `vcov`.
```{r, eval = FALSE}
vcov <-
```

Q-10) Take the covariance of `lifeexp` and `gdppc` and divide by the variance of the `gdppc`. Name it `beta`! 
Hint: check your `vcov` variable and use indexing to get the appropropriate elements.
```{r, eval = FALSE}
beta <-
```

[Back to homeworks](./econ_I_AE_2425.qmd)